Hidden enemy detecting using bayes inference

### 2018-04-17 paper.tex
add discuss about mutiple latent enemy setting

Where $N(x \mid \mu,\sigma)$ is normal probability density function:
$$
N(x \mid \mu,\sigma) = \frac{1}{\sqrt{2\pi \sigma^2}} \exp(\frac{(x-\mu)^2}{2\sigma^2})
$$

@@

%\subsection{Mutiple enempy number setting}
%Maybe removed if time is out.
%\subsection{Enemy movement detecting}
%Maybe removed if time is out.

>>>>

Where $N(x \mid \mu,\sigma)$ is normal probability density function:
$$
N(x \mid \mu,\sigma) = \frac{1}{\sqrt{2\pi \sigma^2}} \exp\left(\frac{(x-\mu)^2}{2\sigma^2}\right)
$$

@@

\subsection{Mutiple enemy number setting}

The above estimation is based on "true" number of enemy. Let we test it's stability. 
What happen if the given number of number of enemy is wrong? The Figure~\ref{fig:bigVb} 
show the result, that flat prior seems well while diagonal prior may may be dominated by 
the prior. But it depict what we want in general.

\begin{figure}[h!]
\includegraphics[width=0.99\linewidth]{big_vb.png}
\label{fig:bigVb}
\end{figure}

\subsubsection{The density of probabity of existence of enemy estimation}

The one of advantage of VB is that it make computation of probability of special region very easy.
The probability of exist of enemy in a given region $[x,x+dx]\times[y,y+dy]$ can be given by:

$$
pe(x,y,dx,dy) = 1 - \prod_i \left(
(1-(\Phi(x+dx - \mu^X_i)/\sigma^X_i) -  (\Phi(x - \mu^X_i)/\sigma^X_i))
(1-(\Phi(y+dy - \mu^Y_i)/\sigma^Y_i) -  (\Phi(y - \mu^Y_i)/\sigma^Y_i))
\right)
$$

Where $\Phi(x)$ is standard cumulative probability function:

$$
\Phi(x) = \int_{-\infty}^x \frac{1}{\sqrt{2\pi}} \exp\left(\frac{x^2}{2}\right)
$$

And $$\mu^X_i$$ is the expect parameter of normal approximated posterior probability of ith enemy.
The three other are same.

The existence density(approximated) is defined:

$$
pe(x,y) = pe(x-\epsilon,y-\epsilon,2\epsilon,2\epsilon)/(4*\epsilon^2)
$$

Where $\epsilon$ is a small number, in there $\epsilon=0.01$. 
The two example can be seen in Figure~\ref{fig:existDensity}. 
The comparing result can be seen in seen in Figure~\ref{fig:bigVbExist}.

\begin{figure}[h!]
\includegraphics[width=0.99\linewidth]{exist_density.png}
\label{fig:existDensity}
\end{figure}

\begin{figure}[h!]
\includegraphics[width=0.99\linewidth]{big_vb_exist_prob.png}
\label{fig:bigVbExist}
\end{figure}

\subsection{Enemy movement detecting}

Considering ally,enemy,battles have not only position, but also have timestamp. In another word,
enemy and ally may move in the time, how do we infer the movement?
